Cache is King: Writing a Blazing-fast Correlation Function Code

### 2014-12-28 paper/ms.tex
Created the code directory structure

\begin{abstract}
We have entered the era of `Big Data' where we are gathering a tremendous amount of data that
needs to be processed as well as modeled accurately. In particular, large galaxy surveys
like the Sloan Digitial Sky Survey requires computing correlation functions. While measuring the
correlation function is not a bottle-neck, modeling the observed galaxy distribution correctly
{\em} requires a MCMC chain and repeated measurements of $\xi(r)$ and/or $\xi(r_p,\pi)$.

@@

\acknowledgments MS acknowledges the fantastic \texttt{largemem} nodes with 1 TB of RAM at Stampede (TACC) without which the project could not have been done. 
This work has been supported by the NSF Career Award (AST-1151650).

@@

\begin{appendix}

>>>>

\begin{abstract}
We have entered the era of `Big Data' where we are gathering a tremendous amount of data that
needs to be processed as well as modeled accurately. In particular, large galaxy surveys
like the Sloan Digitial Sky Survey requires computing correlation functions. While measuring the
correlation function in the data is not a bottle-neck, modeling the observed galaxy distribution correctly
{\em} requires a MCMC chain and repeated measurements of $\xi(r)$ and/or $\xi(r_p,\pi)$.

@@

\section{}

@@
